# Prerequisites {#prerequisites}

In this chapter we get you set up and running with the _twinetverse_, namely the package installation and setting up rtweet to fetch tweets.

## Install

The package can be installed with devtools [@R-devtools] or remotes [@R-remotes], it is available from Github or Bitbucket:

The _twinetverse_ package can be installed from [Github](https://github.com/JohnCoene/twinetverse):

```{r eval=FALSE}
devtools::install_github("JohnCoene/twinetverse")
```

or from [Bitbucket](https://bitbucket.org/JohnCoene/twinetbook/src/master/):

```{r eval=FALSE}
remotes::install_bitbucket("JohnCoene/twinetverse")
```

```{block, type="note"}
In the book we don't explicitly load the package and assume you have it loaded in your environment.
```

```{r eval=FALSE}
library(twinetverse)
```

## Setup rtweet

The rtweet package requires some set up. This is not only extremely easy but also very well explained on rtweet's [official website](http://rtweet.info/articles/auth.html), so head over there if the short description below does not satisfy.

In essence, you will need a Twitter "app" to access its API, to create one:

1. Head over to [apps.twitter.com](https://apps.twitter.com/) and login or signup if you do not have a Twitter account.
2. Click create an app.
3. In the following form, enter an app name, whatever you want, this does not matter.
4. Enter a description, then again, it doesn't matter.
5. Website, simply put a valid website, you can link to your Twitter profile if you do not have one, i.e.: [https://twitter.com/jdatap](https://twitter.com/jdatap)
6. Callback URL, this is **important**, in there put the following: `http://127.0.0.1:1410`, **exactly as is**.

You're now setup with an app, take note of the crendentials of your app under "Keys and Access Tokens", as you will need it to create your token and fetch tweets:

* Consumer Key (`consumer_key`)
* Consumer Secret (`consumer_secret`)
* Access Token (`access_token`)
* Access Token Secret (`access_secret`)

```{block, type = "warn"}
Do **NOT** share those credentials or your token with anyone.
```

Create your token with like so.

```{r, eval=FALSE}
# library(twinetverse)

TK <- create_token(
  "My Application Name",
  consumer_key = "XxxxXxXXxXx",
  consumer_secret = "XxxxXxXXxXx",
  access_token = "XxxxXxXXxXx",
  access_secret = "XxxxXxXXxXx"
)
```

Ideally, also save it. There is no need to re-create a token everytime you want to download data. Once saved you can easily load it `readRDS` (we'll demonstrate that in the next chapter).

```{r, eval = FALSE}
saveRDS(TK, file = "token.rds")
```

You're all set to use the _twinetverse_!