# Get Started {#get-started}

```{r setup, echo=FALSE, include=FALSE}
library(dplyr)
library(twinetverse)

TK <- readRDS("twitter_token.rds")
```

In this chapter we briefly explore the twinetverse: we _collect_ tweets, _build_ and _visualise_ our first graph. The graphs are built with graphTweets (part of the 'verse) which allows building several kinds of graphs, most of which we will explore, however, we will start with a graph that attempts at depicting how users communicate with each other by looking at who \@tags who tweets.

```{block, type = "note"}
If you follow this along in RStudio; the visualisations do not open in the viewer and instead open in your default browser.
```

## Collect

See the [prerequisites](#prerequisites) section if the line below confuses you.

```{r intro read, eval=FALSE}
TK <- readRDS("token.rds")
```

rtweet lets you do a lot of things, however within the context of the _twinetverse_ we mainly use its `search_tweets` to get tweets.

```{r intro collect, eval=TRUE}
tweets <- search_tweets("rstats", token = TK)
```

The `search_tweets` function takes a few arguments some of which we'll eventually get into, above we run the simplest possible call; fetching tweets about "rstats", a reference to the R [@R-base] Twitter [#hashtag](https://twitter.com/search?q=rstats), by default the function returns 100 tweets. Note that we also pass our token to the function.

Each row a is a tweet, rtweet returns quite a lot of variables (`r ncol(tweets)`), we'll only look at a select few.

```{r intro names tweets, eval=TRUE}
names(tweets)
```

## Build

Now we can use the second package part of the _twinetverse_, graphTweets. Again, we'll leave all function's arguments to default to get a simple graph. There's a lot more to the package which we'll uncover progressively as we move through the book.

There are two ways of building a network of Twitter users with graphTweets, the one we use in this book is preferable over the other as it is much more accurate.

1. The more accurate `gt_edges` based on `mentions_screen_name` (names of users \@tagged in tweets) provided by the Twitter API.
2. The less accurate `gt_edges_from_text` which extracts the \@tagged users from the tweets' `text`, essentially the same as `mentions_screen_name` but likely less accurate.

```{r intro edges net, eval=TRUE}
net <- tweets %>% 
  gt_edges(source = screen_name, target = mentions_screen_name)
```

We called `gt_edges` on our `tweets` data.frame, passing a few bare column names. The source of the tweets (the user posting the tweets) will also be the source of our edges so we pass `source = screen_name`, then the target of these edges will be users \@tagged in the tweets, which is given by the API as `mentions_screen_name`; this will be target of our edges.

The object returned is of an unfamiliar class.

```{r intro class of net, eval=TRUE}
class(net)
```

To extracts the results from graphTweets run `gt_collect`, this will work at any point in the chain of pipes (`%>%`).

```{r intro collect net, eval=TRUE}
net <- net %>% 
  gt_collect()

class(net)
```

Great but this returns a lists and R users much prefer data.frames. graphTweets actualy returns two data.frames that are encapsulated in a list. Indeed networks cannot be compressed into a single data.frame, we need 1) nodes and 2) edges.

```{r, eval=TRUE}
names(net)
```

```{block, type = "note"}
A network consists of _nodes_ and _edges_: this is just what graphTweets returns.
```

Great, so it looks like we have both nodes and edges, not really. We only have edges, `net$nodes` is actually `NULL`. 

```{r intro class of nodes and edges, eval=TRUE}
lapply(net, class)
```

In hindsights, we only ran `gt_edges` so it make sense to only have edges. Let's scrap that and get both nodes and edges.

```{r intro redone graph with nodes, eval=TRUE}
net <- tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% # get edges
  gt_nodes() %>% # get nodes
  gt_collect() # collect

lapply(net, class)
```

Before we move on, something to note. graphTweets _requires_ that you run the functions in the correct order, first `gt_edges` and second `gt_nodes`. This is because one can only know the nodes of a graph based on the edges and not vice versa.

```{block, type = "note"}
Run graphTweets' functions in the correct order, first get the edges _then_ the nodes.
```

We have downloaded tweets used them to build a data.frame of nodes and another of edges. Now we're ready to visualise the data.

## Visualise

We can visualise the network with sigmajs. Then again, it's very easy and follows the same idea as graphTweets; we pipe our nodes and edges through. Before we do so, for the sake of clarity, let's unpack our network using the `%<-%` from the Zeallot package [@R-zeallot], imported by the twinetverse.

```{r intro unpack, eval=TRUE}
c(edges, nodes) %<-% net
```

```{block, type = "tip"}
You can always unpack the network with `edges <- net\$edges` and `nodes <- net\$nodes` if you are not comfortable with the above.
```

Let's take a look at the edges.

```{r intro head of edges, eval=FALSE}
head(edges)
```

```{r, eval=TRUE, echo=FALSE}
knitr::kable(head(edges))
```

Each edge simply consists of a `source` and a `target`. In this network, the `source` essentially corresponds to `screen_name` passed in `gt_edges`, it is the user who posted the tweet. In contrast, `target` includes the users that were tagged in the `text` of the tweet. The `n` variable indicates how many tweets connect the `source` to the `target`.

Now let's take a look at the nodes:

```{r intro head of nodes, eval=FALSE}
head(nodes)
```

```{r, eval=TRUE, echo=FALSE}
knitr::kable(head(nodes))
```

In the nodes data frame, the column `n` is the number of times the node appears (whether as `source` or as `target`), while the `nodes` column are the Twitter handles of _both_ the authors of the tweets (`screen_name`) and those who were \@tagged in the tweets. All nodes are of `type` user in this network, but we will have examples later in the book where it may not be.

Below we rename a few columns, to meet sigmajs' naming convention.

1. We add ids to our nodes, this can be a string and thus simply corresponds to our `nodes` column.
2. We essentially rename `n` to `size` as this is what sigmajs understands.
3. We add ids to our edges as sigmajs requires each edge to have a unique id.

```{r intro prep, eval = FALSE}
nodes$id <- as.factor(nodes$nodes) 
nodes$size <- nodes$n 
edges$id <- seq(1, nrow(edges)) 
```

sigmajs has a specific but sensible naming convention as well as basic _minimal requirements_. 

* Nodes must at least include `id`, and `size`.
* Edges must at least include `id`, `source`, and `target`.

Actually, the _twinetverse_ comes with helper functions to prepare the nodes and edges built by graphTweets for use in sigmajs (these are the only functions the 'verse provides).

```{r intro prep twinetverse}
nodes <- nodes2sg(nodes)
edges <- edges2sg(edges)
```

```{block, type = "note"}
You need to respect sigmajs naming convention or the graph will not display.
```

Let's visualise that, we must initialise every sigmajs graph with the `sigmajs` function, then we add our nodes with `sg_nodes`, passing the column names we mentioned previously, `id`, and `size` to meet sigmajs' minimum requirements. *In sigmajs, at the exception of the function called `sigmajs`, all start with `sg_`*  

```{r intro sg nodes, eval=TRUE}
sigmajs() %>% 
  sg_nodes(nodes, id, size) 
```

sigmajs actually allows you to build graphs using only nodes or edges, we'll see why this is useful in a later chapter on [temporal graphs](#temporal). Let's add the edges. Then again, to meet sigmajs' requirements, we pass `id`, `source` and `target`.

```{r intro sg nodes and edges, eval=TRUE}
sigmajs() %>% 
  sg_nodes(nodes, id, size) %>% 
  sg_edges(edges, id, source, target)
```

This graph does not look great. We'll beautify that bit by bit as we move through the book: sigmajs is highly customisable. 

Nevermind beauty, what's on the graph exactly? Each disk/point on the graph is a twitter user, they are connected when one has tagged the other in the a tweet.

You may also notice that the graph contains surprisingly few nodes, given that we queried 100 tweets you would expect over 100 nodes on the graph. This is because our visualisation only includes tweets that mention other users and most tweets are not targeted (tagged) at other users. There is an easy remedy to this which we'll look at in the next section.

```{block, type = "note"}
Remember the workflow of the _twinetverse_:

1. We **collect** the data
2. We **build** the graph
3. We **visualise** the network
```

## Recap

Let's recapitulate before moving on to the next section. The section may look long~ish but the code is not, here it is put together.

```{r intro all code, eval=FALSE}
library(dplyr)

# COLLECT
tweets <- search_tweets("rstats", token = TK)

# BUILD
net <- tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect() 

c(edges, nodes) %<-% net # unpack

# prepare for sigmajs
nodes <- nodes2sg(nodes)
edges <- edges2sg(edges)

# VISUALISE
sigmajs() %>% 
  sg_nodes(nodes, id, size) %>% 
  sg_edges(edges, id, source, target)
```

## Improve

Let's collect more tweets this time, we'll also optimise our Twitter query. This is very useful as the Twitter API (like the vast majority of APIs) limits the amount of data you can access by imposing a [rate limit](https://developer.twitter.com/en/docs/basics/rate-limiting.html). You can always check where you stand with the various Twitter rate limits with `rate_limit()`.

We set `include_rts = FALSE` as we don't need the same tweet multiple times, it does not add information to our graph (currently but it could). We also pass a slightly more sophisticated query to the search tweet endpoint. This is too often overlooked, the Twitter API provides [advanced operators](https://developer.twitter.com/en/docs/tweets/search/guides/standard-operators.html): you are not limited to searching a single keyword every time.

```{block, type="warn"}
Optimise your queries or you'll be hit by frustrating waiting times.
```

We query 1,000 tweets that:

- Include `#rstats`
- Include a [mention](https://help.twitter.com/en/using-twitter/mentions-and-replies) i.e.: `@jdatap`
- Are original (not re-tweets)

Remember to load your token if you're in a new environment.

```{r adv search, eval=TRUE}
# TK <- readRDS(file = "token.rds")
tweets <- search_tweets("#rstats filter:mentions", n = 1000, token = TK, include_rts = FALSE)
```

Let's build the graph, just like we did before. There is more to graphTweets but we won't look into that just yet.

```{r adv net, eval=TRUE}
net <- tweets %>% 
  gt_edges(screen_name, mentions_screen_name) %>% 
  gt_nodes() %>% 
  gt_collect()
```

Let's make a slightly more interesting visualisation this time. First, we'll prepare the data for sigmajs like we did in the [get started](#get-started) chapter.

```{r adv unpack, eval=TRUE}
c(edges, nodes) %<-% net

nodes <- nodes2sg(nodes)
edges <- edges2sg(edges)
```

Now onto the visualisation.

* We add labels that will display on hover by simply passing the `label` column to `sg_nodes`.
* We color the nodes by cluster with `sg_cluster`.
* We layout the graph appropriately using one of igraph's [@R-igraph] many layout algorithms with `sg_layout`.
* We use sigmajs' settings to change the edges color.

```{r adv graph, eval=TRUE}
sigmajs("webgl") %>% 
  sg_nodes(nodes, id, label, size) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout(layout = igraph::layout_components) %>% 
  sg_cluster(
    colors = c(
      "#0075a0",
      "#0084b4",
      "#00aced",
      "#1dcaff",
      "#c0deed"
      )
  ) %>% 
  sg_settings(
    minNodeSize = 1,
    maxNodeSize = 2.5,
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3"
  )
```

Already looking better.
