# Dynamic Edges {#dynamic}

```{r, echo=FALSE, include=FALSE}
library(twinetverse)

TK <- readRDS("twitter_token.rds")
```

So far we have been drawing static graphs, in this chapter we look at dynamic ones, namely temporal. However, being an introduction we'll start with _dynamic edges_ only: we'll plot the nodes and have the edges appear dynamically .We'll tackle the fully temporal network further down the book. 

## Rationale

We've been visualising Twitter interactions in a static manner, but they are dynamic when you think of it. Twitter conversations happen over time, thus far, we've just been drawing all encompassing snapshots. So let's take into account the time factor to make a where the edges appear at different time steps.

## Collect

We'll collect some tweets again, but feel free to use previously collected tweets; nothing changes at this stage.

```{r dyn search, eval=TRUE}
# TK <- readRDS(file = "token.rds")
tweets <- search_tweets("#rstats filter:mentions", n = 5000, token = TK, include_rts = FALSE)
```

## Build

Now onto building the graph.

```{r dyn net, eval=TRUE}
net <- tweets %>% 
  gt_edges(screen_name, mentions_screen_name, created_at) %>% 
  gt_nodes() %>% 
  gt_dyn() %>% 
  gt_collect()
```

Quite a few things differ from previous graphs we have built.

1. We pass `created_at` in `gt_edges`. This in effect adds the `created_at` column to our edges, so that we know the created time of post in which the edge appears.
2. We use `gt_dyn` which stands for `dynamic`, to essentially compute the time at which edges and nodes should appear on the graph.

```{r dyn inspect edges, eval=FALSE}
head(net$edges)
```

```{r, eval=TRUE, echo = FALSE}
knitr::kable(head(net$edges))
```

## Visualise

Now for the visualisation, let's build it step by step; first we prep the data as we did before: renaming a few columns but also running a few unfamiliar computations.

To explain how we build the visualisation, we first need to tell you how the edges will dynamically appear on the graph. The way this works in sigmajs is by specifying the delay in milliseconds before each respective edge should be added. Therefore, we need to transform the date to milliseconds and rescale them to be within a reasonable range: we don't want the edges to actually take 15 days to appear on the graph.

1. We change the date time column (`POSIXct` actually) to a numeric, which gives the number of milliseconds since 1970.
2. We rescale between 0 and 1 then multiply by 10,000 (milliseconds) so that the edges are added over 10 seconds.

```{r dyn unpack}
library(dplyr)

c(edges, nodes) %<-% net # unpack

nodes <- nodes2sg(nodes)

edges <- edges %>% 
  mutate(
    id = 1:n(),
    created_at = as.numeric(created_at),
    created_at = (created_at - min(created_at)) / (max(created_at) - min(created_at)),
    created_at = created_at * 10000
  ) %>% 
  select(id, source, target, created_at)
```

Let's inspect what we obtain.

```{r dyn inspect edges ms, eval=FALSE}
head(net$edges)
```

```{r, eval=TRUE, echo = FALSE}
knitr::kable(head(edges))
```

We see that the column `created_at` has changed from Date time (`POSIXct`) to a numeric. As mentioned previously, we rescaled it to be between 0 and 10,000 milliseconds, let's see if that is correct.

```{r dyn range}
range(edges$created_at)
```

So for instance the edge at row 25, a tweet where \@`r edges$source[25]` tags \@`r edges$target[25]` will appear after `r round(edges$created_at[25])` milliseconds. 

```{r}
edges[25,]
```

Now, the actual visualisation, as mentioned at the begining to the chapter, we'll plot the nodes then add edges dynamically. Let's break it down step by step. 

First, we plot the nodes.

```{r dyn sg nodes}
sigmajs() %>% 
  sg_nodes(nodes, id, size, label) 
```

We'll add the layout as it looks a bit messy with nodes randomly scattered across the canvas. We'll have to compute the layout differently this time, we cannot simply use `sg_layout` as it requires both nodes and edges and we only have nodes on the graph (since edges are to be added later on, dynamically); instead we use `sg_get_layout`.

```{block, type="note"}
You cannot use `sg_cluster` and `sg_layout` in dynamic graphs as they require both nodes and edges, use the `sg_get_*` alternatives.
```

This is something that we had not shared with you earlier on, `sg_nodes` must have `x` and `y` coordinates of each node, however, if missing they are generated randomly by the package. `sg_get_layout` computes the coordinates of the nodes (`x` and `y`) and adds them to our nodes data.frame.

```{r dyn head, warning = FALSE, eval = FALSE}
nodes <- sg_get_layout(nodes, edges)
head(nodes)
```

```{r, warning = FALSE, eval = TRUE, echo=FALSE}
nodes <- sg_get_layout(nodes, edges)

knitr::kable(head(nodes))
```

Now we can simply pass the coordinates `x` and `y` to `sg_nodes`.

```{r dyn nodes 2}
sigmajs() %>% 
  sg_nodes(nodes, id, size, label, x, y) 
```

Let's beautify the graph a little, this deep black is somewhat unnerving.

```{r dynnodes and settings}
sigmajs() %>% 
  sg_nodes(nodes, id, size, label, x, y) %>%
  sg_settings(
    defaultNodeColor = "#127ba3",
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3",
    minNodeSize = 1,
    maxNodeSize = 4,
    minEdgeSize = 0.3,
    maxEdgeSize = 0.3
  )
```

Now we have something that looks like a graph, except it's missing edges. Let's add them.

We add the edges almost exactly as we did before, we use `sg_add_edges` instead of `sg_edges`. Other than the function name, the only difference is that we pass `created_at` as `delay`. We also set `cumsum` to `FALSE` otherwise the function computes the cumulative sum on the `delay`, which is, here, our `created_at` column, and does not require counting the cumulative sum.

```{r dyn nodes and edges}
sigmajs() %>% 
  sg_nodes(nodes, id, size, label, x, y) %>%
  sg_add_edges(edges, created_at, id, source, target, cumsum = FALSE) %>% 
  sg_settings(
    defaultNodeColor = "#127ba3",
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3",
    minNodeSize = 1,
    maxNodeSize = 4,
    minEdgeSize = 0.3,
    maxEdgeSize = 0.3
  )
```

Now the edges appear dynamically. However **you probably missed that** as the animation is triggered when the page is loaded, the edges appear dynamically as you were reading this page. sigmajs provides an easy workaround: we can add a button for the user to trigger the animation themself.

The button is added with `sg_button` to which we pass a label (`Add edges`) and the event (`add_edges`) the button will trigger. The name of the event corresponds to the function it essentially triggers minus the starting `sg_`. In our case `add_edges` triggers `sg_add_edges`. Many events can be triggered by the button, they are listed on sigmajs [official website](http://sigmajs.john-coene.com/articles/buttons.html).  

Click the button in the top right corner of the visualisation to add the edges, it'll take 10 seconds for all of them to be on the graph.

```{r dyn button}
sigmajs() %>% 
  sg_nodes(nodes, id, size, label, x, y) %>%
  sg_add_edges(edges, created_at, id, source, target, cumsum = FALSE) %>% 
  sg_button("Add edges", "add_edges") %>% 
  sg_settings(
    defaultNodeColor = "#127ba3",
    edgeColor = "default",
    defaultEdgeColor = "#d3d3d3",
    minNodeSize = 1,
    maxNodeSize = 4,
    minEdgeSize = 0.3,
    maxEdgeSize = 0.3
  )
```

```{block, type="tip"}
A sigmajs button can trigger multiple events.
```

