# R markdown {#rmd}

This chapter covers R markdown-specific functions of the _twinetverse_.

We've actually covered a few of those already, rtweet and graphTweets do not have functions specifically meant to be used in R markdown, all work just as well in a interactive and non-interactive environments. The dynamic nature of sigmajs, however, suggests the intriduction of additional functions.

## Buttons

One of the functions of the sigmajs package that we have already covered enables adding buttons to make trigger events in sigmajs: `sg_button`. Below are the events that can be tied to buttons.

* `force_start`
* `force_stop`
* `noverlap`
* `drag_nodes`
* `relative_size`
* `add_nodes`
* `add_edges`
* `add_nodes_edges`
* `drop_nodes`
* `drop_edges`
* `animate`
* `export_svg`
* `export_img`

These events need to be tied to the visualisation, the button (`sg_button`) is only the trigger. Most events can be used without triggers, events that cannot just be used on their own are exports: `export_svg` and `export_img`. The events are simply the name of the function (event) they trigger without the starting `sg_`, i.e.: `export_svg` event triggers `sg_export_svg`.

Let's illustrate the above example. We first draw a graph.

```{r}
sigmajs() %>% 
  sg_nodes(nodes, id, size, color) %>% 
  sg_edges(edges, id, source, target)
```

Then add the event and the corresponding button.

```{r}
sigmajs() %>% 
  sg_nodes(nodes, id, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_start() %>% 
  sg_button("start", "force_start")
```
