# Performances {#performances}

```{r, echo=FALSE, include=FALSE}
library(twinetverse)

TK <- readRDS("twitter_token.rds")
```

The graphTweets has already [seen great performance improvements](http://graphtweets.john-coene.com/news/index.html) and can now build large graphs.

The sigmajs library needs some explanation, namely on layout, and renderers.

## Read

You might have noticed that we reduced the number of tweets we visualised in the last four chapters, fetching only 400 odd tweets. This is because dynamic graphs are quite draining for the website (more on that later in the chapter). There is however a remedy to it, or part of it anyway. Instead of using `sg_add_nodes` and `sg_add_edges` we can use the `sg_read_*` family of functions.

We'll collect some tweets setting `type` as `mixed` to ensure we get tweets that spread over a couple of days.

```{r, eval=TRUE}
# TK <- readRDS(file = "token.rds")
tweets <- search_tweets("#rstats", n = 5000, token = TK, include_rts = FALSE, type = "mixed")
```

With the tweets we collected we'll build a dynamic network where nodes and edges appear on the _day_ they are created.

```{r}
graph <- tweets %>% 
	gt_edges(screen_name, mentions_screen_name, created_at) %>% 
	gt_nodes() %>% 
	gt_dyn() %>% 
	gt_collect()

c(edges, nodes) %<-% graph
```

we'll start by changing the `created_at` from a datetime to a date then a numeric. Also, for a change, we'll rescale with the scales package [@R-scales] to rescale the nodes and edges date of appearance, the scales package makes it much more convenient.

```{block, type = "tip"}
You can install `scales` from CRAN with `install.packages("scales")`
```

Note that we also scales package to color the nodes according to their size.

```{r}
nodes <- nodes %>% 
	dplyr::arrange(start) %>% 
	dplyr::mutate(
		start = as.Date(start),
		start = as.integer(start),
		start = scales::rescale(start, to = c(1, 10000)),
		size = n,
		label = nodes,
		color = scales::col_numeric(c("#0075a0", "#c0deed"), domain = NULL,)(start)
	) 

edges <- edges %>% 
	dplyr::arrange(created_at) %>% 
	dplyr::mutate(
		created_at = as.Date(created_at),
		created_at = as.integer(created_at),
		created_at = scales::rescale(created_at, to = c(1, 10000)),
		id = 1:dplyr::n()
	)
```

Now that nodes and edges are ready we can use our new functions, rest assured they work in very much the same way.

```{r}
sigmajs() %>% 
	sg_force_start() %>% 
	sg_read_nodes(nodes, id = nodes, size, label, color, delay = start) %>% 
	sg_read_edges(edges, id, source, target, delay = created_at) %>% 
	sg_force_stop(11000) %>% 
	sg_button(c("read_exec", "force_stop")) %>% 
	sg_read_exec()
```

## Renderers

The sigmajs package actually comes with three renderers out-of-the-box; `canvas`, the default, `svg` and `webgl`. `svg` makes for slightly nicer looking graphs but at performance costs so only use it for the smaller graphs. In contrast, `webgl` is extremely performant.

Let's plot huge graph using `webgl` to demonstrate, below we graph 25,000 nodes.

```{r perf large}
data <- sg_make_nodes_edges(25000) # make 25,000 nodes

sigmajs("webgl") %>% # set to webgl
  sg_nodes(data$nodes, id, size) %>% 
  sg_edges(data$edges, id, source ,target) %>% 
  sg_layout() %>% 
  sg_settings(
    nodeColor = "default",
    defaultNodeColor = "#328983",
    edgeColor = "default",
    defaultEdgeColor = "#b9b9b9"
  )
```

## Layout

As you might have observed in the [previous chapter on ephemeral graphs](#ephemeral) our last graphs is not layed out quite as nicely as we would like to.

**How forceAtlas2 works in sigmajs**

When you pass `sg_force` or `sg_force_start` to your graph, on load (or on the button click, if linked), forceAtlas2 kicks in and starts to layout the graph. We saw that since this is draining the browser we can then pass `sg_force_stop` specifying a `delay` in milliseconds when we want the layout to stop.

What happens when we actually run the above but _adding_ or _dropping_ nodes or edges? In actual fact the layout does not run constantly, as it would not take into account added or dropped nodes or edges and would continue running as if new edges or nodes were not added. Therefore a worker is created and the forceAtlas2 layout is killed then started after every node and or edge is added or dropped. This can be quite difficult for the browser to handle.

Let's make a dummy example below to show how it works smoothly for the smaller graphs.

```{r perf smooth}
nodes <- sg_make_nodes(colors = c("#0084b4", "#00aced", "#1dcaff", "#c0deed"))
edges <- sg_make_edges(nodes)

# add random delay between .5 and 2 seconds
edges$delay <- runif(nrow(edges), 500, 1000) 

sigmajs(height = 300) %>%
  sg_force_start() %>%
  sg_nodes(nodes, id, size, color) %>%
  sg_add_edges(edges, delay, id, source, target, refresh = TRUE) %>% # read delay documentation
  sg_button(c("add_edges"), "Add edges") %>% 
  sg_settings(
    mouseEnabled = FALSE,
	  touchEnabled = FALSE,
    minNodeSize = 1,
    maxNodeSize = 4
  )
```

The above is much less draining on the browser and runs smoothly.